Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-08 paper.tex
another learning curve for strings

   \STATE Draw $e\sim \text{primitives}$, w.p. $\propto\theta_e$ if $e\in \mathcal{D}$
   \STATE \hspace{3.1cm}w.p. $\propto\frac{\theta_{var}}{|\text{variables}|}$ if $e\in \mathcal{E}$
   \STATE Unify $\tau$ with yield$(\tau')$.
   \STATE $\left\{\alpha_k \right\}_{k\leq K}\gets\text{argTypes}(\tau')$
%   \STATE unify$(\tau,\beta)$
   \FOR{$k=1$ {\bfseries to} $K$}
 \STATE $a_k\sim\text{sample}(\mathcal{D},\theta,\mathcal{E},\alpha_k)$
 \ENDFOR
 \STATE \textbf{return} \code{(}$e\;a_1\; a_2\; \cdots\; a_K$\code{)}
 \STATE\textbf{where:}
 \STATE  yield$(\tau) = \begin{cases}
\text{yield}(\beta)   &\text{ if }$\tau = \alpha\to \beta$\\
\tau   &\text{ otherwise.}
 \end{cases}$ 
 \STATE\hspace{0cm} argTypes$(\tau) = \begin{cases}
[\alpha] + \text{argTypes}(\beta)   &\text{ if }$\tau = \alpha\to \beta$\\
[]   &\text{ otherwise.}
 \end{cases}$
\end{algorithmic}
\end{algorithm}

@@

For each domain,
we are interested both in how many tasks the
agent can solve and how quickly it can find those solutions.
For symbolic regression, we also care about the quality
of the solution, as measured by the likelihood model $\probability[x|p]$.
Concretely, this cashes out as measuring how many
real numbers were used in the programs: e.g. did the model correctly explain a linear function
using two numbers, or did it introduce extraneous parameters?
Table~\ref{baselineComparisons}
compares our model against these baselines.
We see that our full model consistently
beats the baselines,
and that the recognition model 
consistently increases the number of solved held-out tasks.
Lesioning the recognition model also slows down the convergence of the algorithm,
taking more wake/sleep cycles to reach a given number of tasks solved (Figure~\ref{learningCurves}).
This data supports our view of the recognition model as a way of accelerating the search over programs.

@@

\begin{figure}\centering
  \includegraphics[width = 7cm]{figures/regression.eps}
  \includegraphics[width = 7cm]{figures/list.eps}
  \includegraphics[width = 7cm]{figures/textLearningCurve.eps}
  \includegraphics[width = 7cm]{figures/circuitLearningCurve.eps}
  \caption{Learning curves for \system both with and without the recognition model (No NN in the above plots). Red: \system. Green: no neural network. Notice how the model without the neural network eventually solves almost all the tasks, but does so using programs with lower likelihood (see Table~\ref{regressionComparison}).}\label{regressionLearningCurve}
\end{figure}

>>>>

   \STATE Draw $e\sim \text{primitives}$, w.p. $\propto\theta_e$ if $e\in \mathcal{D}$
   \STATE \hspace{3.1cm}w.p. $\propto\frac{\theta_{var}}{|\text{variables}|}$ if $e\in \mathcal{E}$
   \STATE Unify $\tau$ with yield$(\tau')$.
   \STATE $\left\{\alpha_k \right\}_{k = 1}^K\gets\text{argTypes}(\tau')$ 
%   \STATE unify$(\tau,\beta)$
   \FOR{$k=1$ {\bfseries to} $K$}
 \STATE $a_k\sim\text{sample}(\mathcal{D},\theta,\mathcal{E},\alpha_k)$
 \ENDFOR
 \STATE \textbf{return} \code{(}$e\;a_1\; a_2\; \cdots\; a_K$\code{)}
 \STATE\textbf{where:}
 \STATE  yield$(\tau) = \begin{cases}
\text{yield}(\beta)   &\text{ if }$\tau = \alpha\to \beta$\\
\tau   &\text{ otherwise.}
 \end{cases}$ 
 \STATE\hspace{0cm} argTypes$(\tau) = \begin{cases}
[\alpha] + \text{argTypes}(\beta)   &\text{ if }$\tau = \alpha\to \beta$\\
[]   &\text{ otherwise.}
 \end{cases}$
\end{algorithmic}
\end{algorithm}

@@

For each domain,
we are interested both in how many tasks the
agent can solve and how quickly it can find those solutions.
For symbolic regression, we also care about the quality
of the solution, as measured by the likelihood model $\probability[x|p]$,
which measures how many
real numbers were used in the program: e.g. did the model correctly explain a linear function
using two numbers, or did it introduce extraneous parameters?
Table~\ref{baselineComparisons}
compares our model against these baselines.
We see that our full model consistently
beats the baselines,
and that the recognition model 
consistently increases the number of solved held-out tasks.
Lesioning the recognition model also slows down the convergence of the algorithm,
taking more wake/sleep cycles to reach a given number of tasks solved (Figure~\ref{learningCurves}).
This data supports our view of the recognition model as a way of accelerating the search over programs.

@@

\begin{figure}\centering
\includegraphics[width = 7cm]{figures/regression.eps}
  \includegraphics[width = 7cm]{figures/list.eps}
  \includegraphics[width = 7cm]{figures/textLearningCurve.eps}
  \includegraphics[width = 7cm]{figures/circuitLearningCurve.eps}  
  \caption{Learning curves for \system both with (blue) and without (red) the recognition model as the frontier size is varied (solid/dashed/dotted lines).}\label{learningCurves} 
\end{figure}
